---
author: "Luba"
title: "wrangling"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Libs

```{r}
library(tidyverse)
library(lubridate)
library(janitor)
library(skimr)
```

# Data dictionary

## Categorical variables

Without missing values!

What is trail and sectors?

We have different **trails** and each Trail have description, name and id. But I don't understand what is this **trail_thread_name/id.**
- Avaliação da Aprendizagem Escolar (trail_name):
  - FOCOS Cursos (trail_thread_name)? This is the where that trail was applied?

Sectors are more intuitive, they follow this structure:

- Modulo 1 (sector_name):
  - Modulo 1: Aula 1 (sector_item_name). Here is normally where you'll find the indication of some activity, called of exam here.

client_id: Just one client ("SAS - Focos"), is who're using the service.
client_name: String indication of the client
trail_*: Explained before
sector_*: Explained before
username: The user accessing the trails and sectors
email: just the personal email of the user
class_name: in case we have student using the platform
status: this is the status of the sector_item? Like: If a finished or not the *Aula 1: Organelas*


## Numerical Variables

- *_ids: Some identification of was showed before
- exam_id: Id of the specific exam applied on the LMS
- year: just the year
- weight: weight of some exame.
  - 4 items, 1 point for each item, final weight equal to 4.
  - 6 items, 3 points for each item, final weight equal to 18
- grade: is how much he/she scored on the test, based on the weight value.
- score: Seems the final score for the user on that exam, based on the got corrected items percentage.
  - 5 items, 1 point each, you got 4 of them correct: 8 is your final score.
- qt_questoes: how many items do we have on that exam. Normally this variable is related to the weight.
  - 6 items, weight 6.
  - 12 items, weight 6. Probably we have each item with 2 points.


## POSIXct

- created_at: To show a timeline of users interaction.


# Questions

- Do we'll have data about the user interaction with the platform?
  - time spent on the item
  - how much time to answer the item
  - how much time in each sector or trail

- We'll have the answer by item?
  - Do we need to look for the exam_id and find the answers by item?
- What happens if the teacher want to put different weights for different items?

# Hypothesis

- How the users are doing on the LMS trails?
- Grade by trails
- Grade by sectors
- Grade by thread trails
- Who more are using the LMS and how he/she is performing on the platform?
- Timeline

# Knowing the data

```{r}
lms_tbl <- read_csv("../data/query_result_2021-08-28T08_00_17.45991Z.csv") %>% clean_names() %>% mutate(client_id = client_id %>% as_factor())

lms_tbl %>% tail() %>% glimpse()

skim(lms_tbl)

# passing some variables to factors
lms_tbl %>% 
  select(grade, score, exam_id, sector_description, created_at) %>% 
  mutate(m = month(created_at)) %>% 
  count(m)
  


```


# TODOs

- remove test users and test activities. Or look for test words in columns!
- answer those hypothesis questions and save the output.